---
title: "Textual Enhancement"
author: "Anonimized for peer review"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    html_document:
      theme: sandstone
      highlight: pygments
      toc: true
      df_print: paged
      code_folding: show
      toc_depth: 4 
      toc_float: 
          collapsed: true
          smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::include_graphics 
```

```{r packages, echo=T, message=F}
pacman::p_load(glmmTMB, # for fitting the Binomial-Gamma Hurdle mixed model
               lme4, # for fitting the `glmer` models 
               emmeans) # for post-hoc comparisons
```

In order to run the codes below, please put the following data files in the folder where this RMD file (i.e., 'TextualEnhancement.Rmd') is located:

- 'AttentionData.rds'
- 'LearningData.rds'

# Research Question 1: Does Textual Enhancement attract attention?

## Best fitting model Q1
```{r, Model for Attention and Skipping}
Q1 <- readRDS(file="AttentionData.rds")
ModelAttention <- glmmTMB(data = Q1,
                        DwellTime ~ (Time * WordCategory) + (1|Participant) + (1|Item), 
                        family = ziGamma(link = "log"),
                        ziformula = ~ (Time * WordCategory) + (1|Participant) + (1|Item)) # binomial part, using the same predictors as the main model 
summary(ModelAttention)
```
## Emmeans Q1
```{r}
EMM1 <- emmeans(ModelAttention, ~ Time*WordCategory, comp = "zi", type = "response") # Calculate EMMs
pairwise_comparisons_1 <- pairs(EMM1)
summary(pairwise_comparisons_1)
```

# Research Question 2: Do participants learn any Dutch vocabulary?

## Best fitting model Q2
```{r, Model for Learning}
Q2 <- readRDS(file="LearningData.rds")
ModelLearning <- glmer(Known ~ Time*WordCategory + PPVTCENT +
            (1 + Time | Participant) +
            (1 | Item),
            data=Q2, family = "binomial")
summary(ModelLearning)
```
## Emmeans Q2
```{r}
EMM2 <- emmeans(ModelLearning, ~ Time*WordCategory, type = "response") # Calculate EMMs
pairwise_comparisons_2 <- pairs(EMM2)
summary(pairwise_comparisons_2)
```

# Research Question 3: Do eye fixations predict learning?

## Best fitting model Q3
```{r, Model for Attention and Learning}
Q3 = Q2[! Q2$WordCategory %in% c("Filler"), ] # to remove the filler category (for which there is no eye data)
Q3 = Q3[! Q3$Item %in% c("vreselijk"), ] # to remove the target word 'vreselijk' which did not occur in the last episode (and for which there is no posttest eye data)
AttentionLearning <- glmer(Known ~ Time * WordCategory + PPVTCENT + Freq_epAll + 
            (1 | Participant) +
            (1 | Item),
            data=Q3,
            family = "binomial")
summary(AttentionLearning)
```

## Emmeans Q3
```{r}
EMM3 <- emmeans(ModelLearning, ~ Time*WordCategory, type = "response") # Calculate EMMs
pairwise_comparisons_3 <- pairs(EMM3)
summary(pairwise_comparisons_3)
```

